Report on Certificate Tools

### 2016-09-20 TEX/draft.tex
Added text to keystore, will add screenshots tommorow.

      \paragraph{Self-signed certificate}
It is possible to generate a key pair and self-signed certificate, simply clic on icon or double clic on blank space, choose algorithm and key length. Then you can choose all the other options such as Basic Constraints and Subject Alternative Name.
%place for screenshots, will do from Windows.
You can also set up deaful pre-fill of Common Name, Organisational Unit, Organisation etc.
%pictures of setting
      \paragraph{Certificate Signing Request}

@@

>>>>

      \paragraph{Self-signed certificate}
It is possible to generate a key pair and self-signed certificate, simply clic on icon or double clic on blank space, choose algorithm and key length. Then you can choose all the other options such as Basic Constraints and Subject Alternative Name.
%place for screenshots, will do from Windows.
You can also set up deaful pre-fill of Common Name, Organisational Unit, Organisation etc.
%pictures of setting
      \paragraph{Certificate Signing Request}
It is possible to make Certificate Signing Request in Keystore Explorer. Simply generate keys and then do not change Basic Constraints v3 part of certificate.      
      \paragraph{Specify length}
Length can be specifyied when making key but ultimately it is confirmed by Certificate Authority when signing a CSR.
      \paragraph{Specify algorithm}
Algorithm is specified when generating keys and also confirmed by certificate authority.
    \subsubsection{Basic constraints}

      \paragraph{Specify Type}
Specifying type is made while generating keys and certificate by changing v3 portion when asked during generation.
      \paragraph{Specify path length}
Specifying of path length is made also by changing v3 part of x509 certificate during generation under Basic Constraints type.
  \subsection{Specifications}

    \subsubsection{Certificate Signing Request signing}
To sign a Certificate Signing Request simply right-click a Certificate Authority certificate and use the sign with option.
    \subsubsection{Create combination of private key and signed chain}

    \subsubsection{Specify certificate validity}
Desired duration of certificate validity is asked during generation, but given whilst signing a Certificate Signing Request by Certificate Authority
    \subsubsection{Setting Subject Alternative Name for end certificates}
Setting of Subject Alternative Name for certificate is made during generation of CSR, under the v3 part of certificate under the Basic Constraints type.
    \subsubsection{Support for Cryptographic Service Provider}
As Far as i know there is not support for using CSP.
\section{Conversions}

@@

    \subsubsection{Certificate or certificate chain from a file}
It is possible to export a certificate from a keystore type by simply right-clicking the chosen certificate and chosing export option.
    \subsubsection{Private key only}
It is possible to export a private key from a keystore type by simply right-clicking the chosen certificate and chosing export->private key option.
  \subsection{Direct conversion between Java Keystore and PKCS\#12 file}

  \subsection{Importing certificates and keys into storage files}
 It is possible to import a certificate and/or key by chosing Import option.
